\chapter{About Modu}

Modu is a web application framework that was developed to address particular
needs I had as a custom web developer.

\section{Features}

\begin{flushleft}
\begin{description}
    \item[Storable API]
    -- Object-relational database database mapper that allows you full
    control of how your model objects are instantiated from database
    content. Create custom models for commonly used tables, or employ a
    standard built-in class for trial use-cases.
    \item[Editable API]
    -- Create powerful customizable admin interfaces. Provide CMS features
    either through an alternate admin interface, or embedded in your public-
    facing web application.
    \item[Pluggable Template System]
    -- Defaults to use the Cheetah Template system, but proof-of-concept
    engines exist supporting CherryTemplate and ZPTPages.
    \item[Implements WSGI]
    -- modu implements the WSGI protocol, and may be installed inside any
    WSGI-compatible web container.
    \item[Form API]
    -- modu forms are heavily inspired by the Drupal Form API, and are
    fully themeable and customizable.
    \item[User/Role/Session support]
    -- DB-resident sessions provide fully customizable user-tracking features
    including built-in support for role-based permissions.
\end{description}
\end{flushleft}

\section{History}

Modu's roots are based in a limited framework I had created to try to deal
with the various problems I was encountering as a PHP developer. When I
moved on to a different position where I had the freedom to choose which
language I used for development, I knew I wanted to use Python, but I missed
some of the features I had gotten accustomed to from my old framework.

Also, I had been loosely affiliated with the Twisted Python project for some
time, and I knew I wanted to use this in my regular development. Unfortunately,
PHP had damaged me more than I liked to admit, and couldn't get comfortable
in the asynchronous world of Twisted.Web development.

I had evaluated a number of Python web frameworks such as Django, TurboGears,
Zope, and CherryPy, but with the sole exception of Zope and Django, I was
completely unimpressed.

Zope and I are simply incompatible; I'd tried it for a variety of small
projects, and was forced to use it for one big one that ended in disaster. This
was almost entirely my fault, due to limitations in my Zope/Plone abilities,
but I didn't think I could trust Zope with my heart again.

As for Django, it's an extremely powerful framework that deserves a close look
by anyone working in this arena, and I don't have a good reason why I didn't
use it. There are some things that I don't particularly like about it, but
nothing I couldn't have gotten over.

In the end, I simply \emph{wanted} to write my own.
