\chapter{Getting Started}

The best way to become familiar with the modu toolkit is to build a sample
site. This chapter will guide you through creating your first modu-based
web project.

The examples in this chapter assume you have a properly configured MySQL 5
server. There is preliminary support for any DB-API 2.0-compliant web server,
but that will not be addressed in this chapter.

\section{Creating A Project Workspace}

The first thing you'll want to do is navigate to a suitable work area, and
use the mkmodu script to create a skeleton project directory.

The various mkmodu command line arguments allow you to specify the project
shortname (required) and two other variables that will be inserted into
comment strings in the resulting output.

\begin{verbatim}
    Usage: mkmodu.py project [options]
    Options:
      -l, --longname=  The descriptive name for the new project.
      -a, --author=    Name of copyright holder.
          --version    
          --help       Display this help and exit.

    Generate a modu project directory.
\end{verbatim}

\subsection{What's Inside a modu Project?}

\begin{figure}[ht]
\label{layout}
\caption{Sample modu project directory layout}
\begin{verbatim}
myproject/
    docs/
        database-schema.mysql
    modu/
        itemdefs/
            page_itemdef.py
            permission_itemdef.py
            role_itemdef.py
            user_itemdef.py
        sites/
            myproject_site.py
    myproject/
        __init__.py
        model/
            __init__.py
            page.py
        resource/
            __init__.py
            index.py
    template/
        index.html.tmpl
    var/
    webroot/
        styles.css
\end{verbatim}
\end{figure}

The resulting directory structure will look something like
figure \ref{layout} on page \pageref{layout}.

\begin{flushleft}
\begin{description}
    \item[\emph{docs/database-schema.mysql}]
    -- A sample database schema, with additional SQL added to create default
    users and other related records
    \item[\emph{modu/itemdefs/}]
    -- Configuration files for the Editable admin interface
    \item[\emph{modu/sites/myproject\_site.py}]
    -- Site configuration file for this project
    \item[\emph{myproject/}]
    -- Top-level package for the classes belonging to this project
    \item[\emph{template/}]
    -- Default root for display templates
    \item[\emph{var/}]
    -- Template cache directory, other transient data
    \item[\emph{webroot/}]
    -- The default webroot for unhandled URLs
\end{description}
\end{flushleft}

\section{Configuring the Database}

After you change to your new project directory, the first thing you'll
need to do is configure the database. You'll need to create a database to
use for the project, and then create a user to access it with.

\begin{flushleft}
\begin{enumerate}
    \item Create the database:
        \begin{verbatim}
        mysql -u root -p -e "CREATE DATABASE myproject;"
        mysql -u root -p -e "GRANT ALL ON myproject.* TO myproject@localhost 
            IDENTIFIED BY 'h7HjkdW2';"
        mysql -u root -p -e "FLUSH PRIVILEGES;"
        \end{verbatim}
    \item Load the generated schema:
        \begin{verbatim}
        mysql -u root -p myproject < docs/database-schema.mysql
        \end{verbatim}
    \item Modify the DB URL specified in \emph{modu/sites/myproject\_site.py} to
        contain the proper SQL login, in the form \verb|driverName://user:password@hostname/dbname|
\end{enumerate}
\end{flushleft}

\section{Launching the modu Server}

Finally, to get the modu webserver up and running, change to your project
directory, and run \verb|twistd -n modu-web| (the -n switch keeps the
application in the foreground, useful in development or debugging).

At this point you should have a functioning modu application running in the
foreground. Connecting to \verb|http://localhost:8888| should display
"Welcome to your new project..."

If you wish to allow the application to daemonize, you can leave off the -n
switch. The pid of the background process will be saved in the current directory.

Many twistd-specific options can be of use here, as well as other UNIX-specific
techniques. Here's an advanced example:

\begin{verbatim}
    su www-data -c "authbind /usr/bin/twistd --logfile=/var/log/modu/error.log
        --pidfile=/var/run/modu/twistd.pid
        modu-web -p 80 --logfile=/var/log/modu/access.log"
\end{verbatim}

You can see the following tricks being used here:

\begin{flushleft}
\begin{enumerate}
    \item This is from an init script, and therefore runs as root, so use
        \verb|su www-data| to run the main server command.
    \item At this point the server is running as www-data, which normally
        isn't allowed to bind to low ports. Use a configured \verb|authbind|
        binary to launch the app with binding privileges.
    \item Since this runs in the background, put the pidfile in a memorable
        location. You'll need this to kill the process later.
    \item Redirect logging to the appropriate places.
    \item Run the server on port 80, instead of the default 8888.
\end{enumerate}
\end{flushleft}


